---
title: "Face-Names Pairs Test (Online)"
author: "Examining individual learning patterns using GLMMs"
date: "Commins et al."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sumPartition <- function(dat,z){
  k <-length(unique(z))
  nobs <- tapply(1:nrow(dat),z,length)
  withinSS <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    sum(xm^2)
    }
  })
  aveD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    mean(xm)
    }
  })
  
  maxD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    max(xm)
    }
  })
  
  part<- data.frame("N.obs"=nobs, "Within clus SS" = withinSS, "Ave dist  Centroid" = aveD,
                    "Max dist centroid" =maxD)
  rownames(part)<- paste("Cluster", 1:k)
  
  return(part)	
}

library(hnp)
library(lme4)
library(tidyverse)
library(ggplot2)
library(readxl)
library(ggrepel)
library(aplpack)
library(car)
library(sp)
library(ape)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

dat <- read_excel("face_names_online.xlsx")

dat$Ps <- as.factor(dat$Ps)
dat$FN <- as.factor(dat$FN)
```

## Exploratory analysis

```{r, warning = FALSE, message = FALSE, echo = FALSE}
dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score (%)") +
  geom_smooth() +
  ylim(0, 100) +
  facet_wrap(~ FN)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100, colour = FN)) +
  theme_bw() +
  xlab("Trial") +
  ylab("Score (%)") +
  geom_smooth(se = FALSE) +
  ylim(0, 100)
```

## Modelling

We fitted a binomial generalized linear mixed model. We included a different linear effect of Trial per FN class in the linear predictor, and random intercepts and slopes per individual. Below we present the estimated coefficients, estimated variance-covariance matrix and curve.

```{r, echo = FALSE}
fit1 <- glmer(cbind(Score, total - Score) ~ Trial * FN +
                (Trial || FN:Ps),
              family = binomial,
              data = dat)
summary(fit1)

fit2 <- glmer(cbind(Score, total - Score) ~ Trial * FN +
               (1 | FN:Ps),
             family = binomial,
             data = dat)

anova(fit1, fit2, test = "Chisq")

drop1(fit1, test = "Chisq")

fit <- glmer(cbind(Score, total - Score) ~ 0 + FN + Trial : FN +
               (Trial || FN:Ps),
             family = binomial,
             data = dat)

beta_hat <- fixef(fit)
V <- vcov(fit)
dat_pred <- expand.grid(Trial = seq(1, 4, length = 200),
                        FN = levels(dat$FN)) %>%
  as_tibble
X_pred <- model.matrix(~ 0 + FN + Trial : FN, data = dat_pred)
dat_pred$pred <- plogis(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- plogis(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- plogis(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  facet_wrap(~ FN)

dat %>%
  ggplot(aes(x = Trial, colour = FN, fill = FN)) +
  theme_bw() +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              alpha = .2, col = NA)
```

Individual curves:

```{r, fig.height=10}
dat_pred_ind <- expand.grid(Trial = seq(1, 4, length = 200),
                            FN = levels(dat$FN),
                            Ps = levels(dat$Ps))
dat_pred_ind$pred <- predict(fit1, dat_pred_ind, type = "response")

dat %>%
  filter(FN == "massed") %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line() +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred_ind %>%
              filter(FN == "massed"),
            aes(y = pred * 100),
            col = 4) +
  facet_wrap(~ Ps) +
  ggtitle("Massed")

dat %>%
  filter(FN == "spaced") %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line() +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred_ind %>%
              filter(FN == "spaced"),
            aes(y = pred * 100),
            col = 4) +
  facet_wrap(~ Ps) +
  ggtitle("Spaced")
```

Now we look at the distribution of the random effects. They seem to follow a normal distribution:

```{r, echo = FALSE}
ran <- ranef(fit)$`FN:Ps` %>%
  as_tibble %>%
  mutate(FN_ID = rownames(ranef(fit)$`FN:Ps`)) %>%
  mutate(FN = sub(":.*", "", FN_ID),
         ID = sub(".*:", "", FN_ID)) %>%
  select(- FN_ID)

names(ran)[1:2] <- c("intercept","slope")

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Let's isolate the individuals with the lowest and highest 5\% intercepts and slopes.

```{r, echo = FALSE}
lower_int_massed <- ran %>%
  filter(FN == "massed") %>%
  filter(intercept <= quantile(intercept, .05)) %>%
  pull(ID)
upper_int_massed <- ran %>%
  filter(FN == "massed") %>%
  filter(intercept >= quantile(intercept, .95)) %>%
  pull(ID)

lower_slo_massed <- ran %>%
  filter(FN == "massed") %>%
  filter(slope <= quantile(slope, .05)) %>%
  pull(ID)
upper_slo_massed <- ran %>%
  filter(FN == "massed") %>%
  filter(slope >= quantile(slope, .95)) %>%
  pull(ID)

lower_int_spaced <- ran %>%
  filter(FN == "spaced") %>%
  filter(intercept <= quantile(intercept, .05)) %>%
  pull(ID)
upper_int_spaced <- ran %>%
  filter(FN == "spaced") %>%
  filter(intercept >= quantile(intercept, .95)) %>%
  pull(ID)

lower_slo_spaced <- ran %>%
  filter(FN == "spaced") %>%
  filter(slope <= quantile(slope, .05)) %>%
  pull(ID)
upper_slo_spaced <- ran %>%
  filter(FN == "spaced") %>%
  filter(slope >= quantile(slope, .95)) %>%
  pull(ID)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  geom_line(data = dat %>%
              filter(FN == "massed" & Ps %in% lower_int_massed),
            aes(group = Ps), col = 2) +
  geom_line(data = dat %>%
              filter(FN == "spaced" & Ps %in% lower_int_spaced),
            aes(group = Ps), col = 2) +
  ggtitle("In red -- lowest 5% intercepts",
          subtitle = paste("(Massed) ID no.: ", paste(lower_int_massed, collapse = ", "), "\n(Spaced) ID no.: ", paste(lower_int_spaced, collapse = ", "))) +
  facet_wrap(~ FN)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  geom_line(data = dat %>%
              filter(FN == "massed" & Ps %in% upper_int_massed),
            aes(group = Ps), col = 2) +
  geom_line(data = dat %>%
              filter(FN == "spaced" & Ps %in% upper_int_spaced),
            aes(group = Ps), col = 2) +
  ggtitle("In red -- highest 5% intercepts",
          subtitle = paste("(Massed) ID no.: ", paste(upper_int_massed, collapse = ", "), "\n(Spaced) ID no.: ", paste(upper_int_spaced, collapse = ", "))) +
  facet_wrap(~ FN)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  geom_line(data = dat %>%
              filter(FN == "massed" & Ps %in% lower_slo_massed),
            aes(group = Ps), col = 2) +
  geom_line(data = dat %>%
              filter(FN == "spaced" & Ps %in% lower_slo_spaced),
            aes(group = Ps), col = 2) +
  ggtitle("In red -- lowest 5% slopes",
          subtitle = paste("(Massed) ID no.: ", paste(lower_slo_massed, collapse = ", "), "\n(Spaced) ID no.: ", paste(lower_slo_spaced, collapse = ", "))) +
  facet_wrap(~ FN)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  geom_line(data = dat %>%
              filter(FN == "massed" & Ps %in% upper_slo_massed),
            aes(group = Ps), col = 2) +
  geom_line(data = dat %>%
              filter(FN == "spaced" & Ps %in% upper_slo_spaced),
            aes(group = Ps), col = 2) +
  ggtitle("In red -- highest 5% slopes",
          subtitle = paste("(Massed) ID no.: ", paste(upper_slo_massed, collapse = ", "), "\n(Spaced) ID no.: ", paste(upper_slo_spaced, collapse = ", "))) +
  facet_wrap(~ FN)
```

Identifying outliers using a bivariate normal distribution:

```{r, echo = FALSE}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  facet_wrap(~ FN)
```

Labelling only points out of the 85% ellipse:

```{r, echo = FALSE}
build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
points2 <- build[[1]] %>% filter(PANEL == 2) %>% dplyr::select(x,y)
ell1 <- build[[7]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell2 <- build[[7]] %>% filter(PANEL == 2) %>% dplyr::select(x,y)

ell_massed <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))
ell_spaced <- which(as.logical(1 - point.in.polygon(points2$x, points2$y, ell2$x, ell2$y)))

ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(FN == "massed" & ID %in% ell_massed),
                  aes(label = ID), force = .25) +
  geom_text_repel(data = ran %>%
                    filter(FN == "spaced" & ID %in% ell_spaced),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95, lty = 2, col = 4) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  facet_wrap(~ FN) +
  coord_equal()
```

## Calculating ellipse stats

```{r}
ellipse_massed <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ellipse_spaced <- build[[5]] %>% filter(PANEL == 2) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ellipse_centre_massed <- c(mean(ellipse_massed$x),mean(ellipse_massed$y))
distances_massed <- apply(ellipse_massed, 1, function(x) dist_2_points(x, ellipse_centre_massed))

a_massed <- max(distances_massed)
b_massed <- min(distances_massed)
area_massed <- pi * a_massed * b_massed
axis_ratio_massed <- a_massed / b_massed
ecc_massed <- sqrt(1 - b_massed^2/a_massed^2)

ellipse_centre_spaced <- c(mean(ellipse_spaced$x),mean(ellipse_spaced$y))
distances_spaced <- apply(ellipse_spaced, 1, function(x) dist_2_points(x, ellipse_centre_spaced))

a_spaced <- max(distances_spaced)
b_spaced <- min(distances_spaced)
area_spaced <- pi * a_spaced * b_spaced
axis_ratio_spaced <- a_spaced / b_spaced
ecc_spaced <- sqrt(1 - b_spaced^2/a_spaced^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(FN == "massed" & ID %in% ell_massed),
                  aes(label = ID), force = .25) +
  geom_text_repel(data = ran %>%
                    filter(FN == "spaced" & ID %in% ell_spaced),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("Massed: area = ", round(area_massed, 3),
                        "; eccentricity = ", round(ecc_massed, 3),
                        "\nSpaced: area = ", round(area_spaced, 3),
                        "; eccentricity = ", round(ecc_spaced, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95, lty = 2, col = 4) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  facet_wrap(~ FN) +
  coord_equal() +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

ggsave("spaced_massed_new.png", dpi = 800, units = "in", w = 8, h = 5)
```

## Comparing observed versus expected frequencies in each quadrant

```{r}
which_quadrant <- Vectorize(function(x, y) {
  if(x >= 0) {
    if(y >= 0) {
      q <- "Q1"
    } else {
      q <- "Q2"
    }
  } else {
    if(y >= 0) {
      q <- "Q4"
    } else {
      q <- "Q3"
    }
  }
  return(q)
})

ran2 <- ran %>%
  mutate(quadrant = which_quadrant(intercept, slope))

freq_table <- xtabs(~ FN + quadrant, data = ran2)

y <- as.numeric(freq_table)
FN <- factor(rep(c("massed","spaced"), 4))
quadrant <- factor(rep(c("Q1","Q2","Q3","Q4"), each = 2))

mod <- glm(y ~ FN * quadrant, family = poisson)
anova(mod, test = "Chisq")

chisq.test(freq_table, simulate.p.value = TRUE, B = 10000)
```

## Clustering based on random effects

```{r, warning = FALSE, message = FALSE}
ran_mat <- as.matrix(ran[,1:2])
rownames(ran_mat) <- factor(substr(ran$FN, 1, 1)) : factor(ran$ID)
#rownames(ran_mat) <- substr(rownames(ran_mat), 1, 1)
ran_dist <- dist(ran_mat)
ran_clust <- hclust(ran_dist, method = "ward.D2")
clus2 <- cutree(ran_clust, 6)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust), type = "fan",
     tip.color = cols[as.numeric(ran$FN == "massed") + 1],
     font = 1,
     edge.width = .7)

dat$FNPs <- dat$FN : dat$Ps
dat$cluster <- as.factor(as.character(dat$FNPs))
levels(dat$cluster) <- paste("Cluster", clus2)

dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = FN:Ps, colour = FN), alpha = .5) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  facet_wrap(~ cluster) +
  geom_smooth(se = FALSE)
```

Clustering per condition:

```{r, warning = FALSE, message = FALSE}
ran_mat_massed <- ran_mat[1:179,]
ran_dist_massed <- dist(ran_mat_massed)
ran_clust_massed <- hclust(ran_dist_massed, method = "ward.D2")
clus2_massed <- cutree(ran_clust_massed, 6)
cols <- gg_color_hue(6)

plot(as.phylo(ran_clust_massed), type = "fan",
     tip.color = cols[clus2_massed],
     font = 1,
     edge.width = .7)

dat_massed <- dat %>% filter(FN == "massed")
dat_massed$cluster <- as.factor(as.character(dat_massed$Ps))
levels(dat_massed$cluster) <- paste("Cluster", clus2_massed)

dat_massed %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  facet_wrap(~ cluster) +
  geom_smooth(se = FALSE) +
  ggtitle("Massed")

ran_mat_spaced <- ran_mat[180:358,]
ran_dist_spaced <- dist(ran_mat_spaced)
ran_clust_spaced <- hclust(ran_dist_spaced, method = "ward.D2")
clus2_spaced <- cutree(ran_clust_spaced, 6)
cols <- gg_color_hue(6)

plot(as.phylo(ran_clust_spaced), type = "fan",
     tip.color = cols[clus2_spaced],
     font = 1,
     edge.width = .7)

dat_spaced <- dat %>% filter(FN == "spaced")
dat_spaced$cluster <- as.factor(as.character(dat_spaced$Ps))
levels(dat_spaced$cluster) <- paste("Cluster", clus2_spaced)

dat_spaced %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  facet_wrap(~ cluster) +
  geom_smooth(se = FALSE) +
  ggtitle("Spaced")
```

Checking Total Within-Cluster Sum of Squares.

```{r}
twss_massed <- twss_spaced <- NULL
for(i in 1:10) {
  twss_massed[i] <- sum(sumPartition(ran_mat_massed, cutree(ran_clust_massed, i))[,2])
  twss_spaced[i] <- sum(sumPartition(ran_mat_spaced, cutree(ran_clust_spaced, i))[,2])
}

plot(twss_massed, type = "b")
lines(twss_spaced, type = "b", col = 2)
```

## Figure 1 parts (a) and (b)

```{r}
fig1_a <- dat %>%
  ggplot(aes(x = Trial, y = Score/total * 100)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score (%)") +
  ylim(0, 100) +
  geom_line(data = dat_pred, aes(y = pred * 100),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred * 100, ymin = lower * 100, ymax = upper * 100),
              fill = 4, alpha = .2) +
  facet_wrap(~ FN) +
  ggtitle("(a)")

fig1_b <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(FN == "massed" & ID %in% ell_massed),
                  aes(label = ID), force = .25) +
  geom_text_repel(data = ran %>%
                    filter(FN == "spaced" & ID %in% ell_spaced),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("(b)",
          subtitle = paste0("Massed: area = ", round(area_massed, 3),
                        "; eccentricity = ", round(ecc_massed, 3),
                        "\nSpaced: area = ", round(area_spaced, 3),
                        "; eccentricity = ", round(ecc_spaced, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95, lty = 2, col = 4) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  facet_wrap(~ FN) +
  coord_equal() +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")
```