---
title: "Sea Hero Quest"
author: "Examining individual learning patterns using GLMMs"
date: "Commins et al."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sumPartition <- function(dat,z){
  k <-length(unique(z))
  nobs <- tapply(1:nrow(dat),z,length)
  withinSS <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    sum(xm^2)
    }
  })
  aveD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    mean(xm)
    }
  })
  
  maxD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    max(xm)
    }
  })
  
  part<- data.frame("N.obs"=nobs, "Within clus SS" = withinSS, "Ave dist  Centroid" = aveD,
                    "Max dist centroid" =maxD)
  rownames(part)<- paste("Cluster", 1:k)
  
  return(part)	
}

library(hnp)
library(lme4)
library(tidyverse)
library(ggplot2)
library(readxl)
library(ggrepel)
library(aplpack)
library(car)
library(sp)
library(gamlss)
library(ape)
library(glmmTMB)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

dat <- read_csv("sea_hero_quest.csv")

dat$Ps <- as.factor(dat$Ps)
dat$Age <- as.factor(dat$Age)
```

## Exploratory analysis

```{r, warning = FALSE, message = FALSE, echo = FALSE}
dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ Age, scales = "free_y")

dat %>%
  ggplot(aes(x = Trial, y = Score, colour = Age)) +
  theme_bw() +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(se = FALSE)
```

## Modelling

We fitted a gamma generalized linear mixed model. We included different smooth effects of Trial per Age group in the linear predictor for the mean and dispersion parameters. Both mean and dispersion were modelled with a log link. Below we present the estimated coefficients, estimated variance-covariance matrix and curve.

```{r, echo = FALSE}
dat$AgePs <- dat$Age : dat$Ps

fit1 <- glmmTMB(Score ~ bs(scale(Trial, 3)) * Age + (bs(scale(Trial), 3) || AgePs),
                dispformula = ~ bs(scale(Trial, 3)) * Age,
                family = Gamma(link = log),
                data = dat)

summary(fit1)
```

Diagnostics:

```{r}
ran <- ranef(fit1)$cond$AgePs %>% as_tibble
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,4))
hnp(ran$`(Intercept)`, scale = TRUE, main = "intercept")
hnp(ran$`bs(scale(Trial), 3)1`, scale = TRUE, main = "bs_1")
hnp(ran$`bs(scale(Trial), 3)2`, scale = TRUE, main = "bs_2")
hnp(ran$`bs(scale(Trial), 3)3`, scale = TRUE, main = "bs_3")
hist(ran$`(Intercept)`, prob = TRUE, main = "intercept")
lines(density(ran$`(Intercept)`))
curve(dnorm(x, 0, sd(ran$`(Intercept)`)), add = TRUE, col = 4, lwd = 2)
hist(ran$`bs(scale(Trial), 3)1`, prob = TRUE, main = "bs_1")
lines(density(ran$`bs(scale(Trial), 3)1`))
curve(dnorm(x, 0, sd(ran$`bs(scale(Trial), 3)1`)), add = TRUE, col = 4, lwd = 2)
hist(ran$`bs(scale(Trial), 3)2`, prob = TRUE, main = "bs_2")
lines(density(ran$`bs(scale(Trial), 3)2`))
curve(dnorm(x, 0, sd(ran$`bs(scale(Trial), 3)2`)), add = TRUE, col = 4, lwd = 2)
hist(ran$`bs(scale(Trial), 3)3`, prob = TRUE, main = "bs_3")
lines(density(ran$`bs(scale(Trial), 3)3`))
curve(dnorm(x, 0, sd(ran$`bs(scale(Trial), 3)3`)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- fixef(fit1)$cond
V <- vcov(fit1)$cond
dat_pred <- expand.grid(Trial = seq(1, 5, length = 200),
                        Age = levels(dat$Age)) %>%
  as_tibble
X_pred <- model.matrix(~ bs(scale(Trial), 3) * Age, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .1) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = .5) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .5) +
  facet_wrap(~ Age, scales = "free_y")

dat %>%
  ggplot(aes(x = Trial, colour = Age, fill = Age)) +
  theme_bw() +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              alpha = .2, col = NA)
```

Individual curves:

```{r, fig.height=20, fig.width=12}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ AgePs, ncol = 12)
```

Clustering.

```{r, fig.width=6, fig.height=6}
ran_mat <- as.matrix(ran)
rownames(ran_mat) <- rep(levels(dat$Age), each = 60)
ran_dist <- dist(ran_mat)
ran_clust <- hclust(ran_dist, method = "ward.D2")
clus2 <- cutree(ran_clust, 4)
cols <- gg_color_hue(4)

plot(as.phylo(ran_clust), type = "fan",
     tip.color = cols[as.numeric(as.factor(rownames(ran_mat)))],
     font = 1,
     edge.width = .7)
```

```{r}
dat$cluster <- as.factor(as.character(dat$AgePs))
levels(dat$cluster) <- paste("Cluster", clus2)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = AgePs, colour = Age), alpha = .7) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ cluster)
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss <- NULL
for(i in 1:10) {
  twss[i] <- sum(sumPartition(ran_mat, cutree(ran_clust, i))[,2])
}

plot(twss, type = "b")
```

## Figure 3

```{r}
twss_plot <- tibble(twss = twss,
                    nclust = 1:10)

dendro_data_k <- function(hc, k) {
  
  hcdata    <-  ggdendro::dendro_data(hc, type = "rectangle")
  seg       <-  hcdata$segments
  labclust  <-  cutree(hc, k)[hc$order]
  segclust  <-  rep(0L, nrow(seg))
  heights   <-  sort(hc$height, decreasing = TRUE)
  height    <-  mean(c(heights[k], heights[k - 1L]), na.rm = TRUE)
  
  for (i in 1:k) {
    xi      <-  hcdata$labels$x[labclust == i]
    idx1    <-  seg$x    >= min(xi) & seg$x    <= max(xi)
    idx2    <-  seg$xend >= min(xi) & seg$xend <= max(xi)
    idx3    <-  seg$yend < height
    idx     <-  idx1 & idx2 & idx3
    segclust[idx] <- i
  }
  
  idx                    <-  which(segclust == 0L)
  segclust[idx]          <-  segclust[idx + 1L]
  hcdata$segments$clust  <-  segclust
  hcdata$segments$line   <-  as.integer(segclust < 1L)
  hcdata$labels$clust    <-  labclust
  
  hcdata
}

set_labels_params <- function(nbLabels,
                              direction = c("tb", "bt", "lr", "rl"),
                              fan       = FALSE) {
  if (fan) {
    angle       <-  360 / nbLabels * 1:nbLabels + 90
    idx         <-  angle >= 90 & angle <= 270
    angle[idx]  <-  angle[idx] + 180
    hjust       <-  rep(0, nbLabels)
    hjust[idx]  <-  1
  } else {
    angle       <-  rep(0, nbLabels)
    hjust       <-  0
    if (direction %in% c("tb", "bt")) { angle <- angle + 45 }
    if (direction %in% c("tb", "rl")) { hjust <- 1 }
  }
  list(angle = angle, hjust = hjust, vjust = 0.5)
}

plot_ggdendro <- function(hcdata,
                          direction   = c("lr", "rl", "tb", "bt"),
                          fan         = FALSE,
                          scale.color = NULL,
                          branch.size = 1,
                          label.size  = 3,
                          nudge.label = 0.01,
                          expand.y    = 0.1) {
  
  direction <- match.arg(direction) # if fan = FALSE
  ybreaks   <- pretty(segment(hcdata)$y, n = 5)
  ymax      <- max(segment(hcdata)$y)
  
  ## branches
  p <- ggplot() +
    geom_segment(data         =  segment(hcdata),
                 aes(x        =  x,
                     y        =  y,
                     xend     =  xend,
                     yend     =  yend,
                     colour   =  factor(clust)),
                 lineend      =  "round",
                 show.legend  =  FALSE,
                 size         =  branch.size)
  
  ## orientation
  if (fan) {
    p <- p +
      coord_polar(direction = -1) +
      scale_x_continuous(breaks = NULL,
                         limits = c(0, nrow(label(hcdata)))) +
      scale_y_reverse(breaks = ybreaks)
  } else {
    p <- p + scale_x_continuous(breaks = NULL)
    if (direction %in% c("rl", "lr")) {
      p <- p + coord_flip()
    }
    if (direction %in% c("bt", "lr")) {
      p <- p + scale_y_reverse(breaks = ybreaks)
    } else {
      p <- p + scale_y_continuous(breaks = ybreaks)
      nudge.label <- -(nudge.label)
    }
  }
  
  # labels
  labelParams <- set_labels_params(nrow(hcdata$labels), direction, fan)
  hcdata$labels$angle <- labelParams$angle
  
  p <- p +
    geom_text(data        =  label(hcdata),
              aes(x       =  x,
                  y       =  y,
                  label   =  label,
                  colour  =  factor(label),
                  angle   =  angle),
              vjust       =  labelParams$vjust,
              hjust       =  labelParams$hjust,
              nudge_y     =  ymax * nudge.label,
              size        =  label.size,
              show.legend =  FALSE)
  
  if (!is.null(scale.color)) {
    p <- p + scale_color_manual(values = scale.color)
  }
  
  ylim <- -round(ymax * expand.y, 1)
  p    <- p + expand_limits(y = ylim)
  
  p
}

dend_col <- gg_color_hue(4)
ddata <- dendro_data_k(ran_clust, 4)

fig3_a <- dat %>%
  ggplot(aes(x = Trial, colour = Age, fill = Age)) +
  theme_bw() +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              alpha = .2, col = NA) +
  ggtitle("(a)")

fig3_b <- dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = AgePs, colour = Age), alpha = .7) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ cluster) +
  ggtitle("(b)")

fig3_c <- plot_ggdendro(ddata,
              fan = TRUE,
              label.size = 2,
              expand.y = .1,
              scale.color = c(1,1,dend_col[1],1,dend_col[2],1,1,dend_col[3],dend_col[4]),
              branch.size = .4) +
  theme_void() +
  ggtitle("(c)")

fig3_d <- twss_plot %>%
  filter(nclust <= 7) %>%
  ggplot(aes(y = twss, x = nclust)) +
  theme_bw() +
  geom_point() +
  geom_line() +
  xlab("Number of clusters") +
  ylab("TWSS") +
  scale_x_continuous(breaks = 1:7) +
  ggtitle("(d)")
```