---
title: "Virtual Navigation Task"
author: "Examining individual learning patterns using GLMMs"
date: "Commins et al."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sumPartition <- function(dat,z){
  k <-length(unique(z))
  nobs <- tapply(1:nrow(dat),z,length)
  withinSS <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    sum(xm^2)
    }
  })
  aveD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    mean(xm)
    }
  })
  
  maxD <- tapply(1:nrow(dat),z,function(i){
    if (length(i)==1) 0
    else {x<- dat[i,]
    xm <- scale(x, scale=F)
    xm <- apply(xm, 1, function(y) sqrt(sum(y^2)))
    max(xm)
    }
  })
  
  part<- data.frame("N.obs"=nobs, "Within clus SS" = withinSS, "Ave dist  Centroid" = aveD,
                    "Max dist centroid" =maxD)
  rownames(part)<- paste("Cluster", 1:k)
  
  return(part)	
}

library(hnp)
library(lme4)
library(tidyverse)
library(ggplot2)
library(readxl)
library(ggrepel)
library(aplpack)
library(car)
library(sp)
library(gamlss)
library(gamlss.cens)
library(ape)
library(ggdendro)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

dat <- read_csv("virtual_navigation_task.csv")

dat$Ps <- as.factor(dat$Ps)
dat$cens <- ifelse(dat$Score == 60, 0, 1)
```

## Exploratory analysis

```{r, warning = FALSE, message = FALSE, echo = FALSE}
dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4)

dat %>%
  group_by(Trial) %>%
  summarise(variance = var(Score)) %>%
  ggplot(aes(x = Trial, y = log(variance))) +
  theme_bw() +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")
```

## Modelling

We fitted a right-censored Gamma mixed model. We included different linear effects of Trial in the linear predictor for the mean parameter, and random intercepts and slopes per individual. We also included the linear effect of Trial in the linear predictor for the dispersion parameter. Both mean and dispersion were modelled with a log link. Below we present the estimated coefficients, estimated variance-covariance matrix and curve.

```{r, echo = FALSE}
gen.cens(GA)

fit1 <- gamlss(Surv(time = Score, event = cens, type = "right") ~
                 Trial + re(random = list(Ps = pdDiag(~ Trial))),
               sigma.formula = ~ Trial,
               family = cens(GA),
               data = dat)
summary(fit1)

getSmo(fit1)
```

Diagnostics:

```{r}
wp(fit1)

ran <- ranef(getSmo(fit1)) %>% as_tibble
names(ran) <- c("intercept","slope")
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- coef(fit1)[-length(coef(fit1))]
V <- vcov(fit1)[1:2,1:2]
dat_pred <- expand.grid(Trial = seq(1, 12, length = 200)) %>%
  as_tibble
X_pred <- model.matrix(~ Trial, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2)

fig3_a <- dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2) +
  scale_x_continuous(breaks = 1:12) +
  ggtitle("(a) Scores over time")

```

Individual curves:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Producing ellipsoids.

```{r}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  xlab("Intercept") +
  ylab("Slope")

build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell1 <- build[[6]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

ell_1 <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))

ell1 <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ell1_centre <- c(mean(ell1$x),mean(ell1$y))
dist_ell1 <- apply(ell1, 1, function(x) dist_2_points(x, ell1_centre))

a_ell1 <- max(dist_ell1)
b_ell1 <- min(dist_ell1)
area_ell1 <- pi * a_ell1 * b_ell1
axis_ratio_ell1 <- a_ell1 / b_ell1
ecc_ell1 <- sqrt(1 - b_ell1^2/a_ell1^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

#ggsave("continuous_censored_new.png", dpi = 800, units = "in", w = 6, h = 5)

fig3_b <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("(b) Bivariate ellipsoid",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")
```

In blue the individuals with outlying behaviour:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  geom_line(data = dat %>%
              filter(Ps %in% ell_1),
            aes(y = exp(pred)),
            col = 4) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

## Clustering based on random effects

```{r}
ran_dist112 <- dist(ran[,1:2])
ran_clust112 <- hclust(ran_dist112, method = "ward.D2")
clus2112 <- cutree(ran_clust112, 2)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust112), type = "fan",
     tip.color = cols[clus2112],
     font = 1,
     edge.width = .7)

dat$cluster <- dat$Ps
levels(dat$cluster) <- paste("Cluster", clus2112)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ cluster)

fig3_c <- dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4, se = FALSE) +
  facet_wrap(~ cluster) +
  scale_x_continuous(breaks = 1:12) +
  ggtitle("(c) Clustering")
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss1 <- NULL
for(i in 1:10) {
  twss1[i] <- sum(sumPartition(ran[,1:2], cutree(ran_clust112, i))[,2])
}

plot(twss1, type = "b")
```

## Re-running everything stopping at different trial numbers

### Stopping at trial 4

```{r}
dat <- read_csv("virtual_navigation_task.csv")

dat$Ps <- as.factor(dat$Ps)
dat$cens <- ifelse(dat$Score == 60, 0, 1)

dat <- dat %>%
  filter(Trial <= 4)
```

```{r, echo = FALSE}
gen.cens(GA)

fit1 <- gamlss(Surv(time = Score, event = cens, type = "right") ~
                 Trial + re(random = list(Ps = pdDiag(~ Trial))),
               sigma.formula = ~ Trial,
               family = cens(GA),
               data = dat)
summary(fit1)

getSmo(fit1)
```

Diagnostics:

```{r}
wp(fit1)

ran <- ranef(getSmo(fit1)) %>% as_tibble
names(ran) <- c("intercept","slope")
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- coef(fit1)[-length(coef(fit1))]
V <- vcov(fit1)[1:2,1:2]
dat_pred <- expand.grid(Trial = seq(1, 12, length = 200)) %>%
  as_tibble
X_pred <- model.matrix(~ Trial, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2)
```

Individual curves:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Producing ellipsoids.

```{r}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  xlab("Intercept") +
  ylab("Slope")

build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell1 <- build[[6]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

ell_1 <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))

ell1 <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ell1_centre <- c(mean(ell1$x),mean(ell1$y))
dist_ell1 <- apply(ell1, 1, function(x) dist_2_points(x, ell1_centre))

a_ell1 <- max(dist_ell1)
b_ell1 <- min(dist_ell1)
area_ell1 <- pi * a_ell1 * b_ell1
axis_ratio_ell1 <- a_ell1 / b_ell1
ecc_ell1 <- sqrt(1 - b_ell1^2/a_ell1^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

#ggsave("continuous_censored_new_t4.png", dpi = 800, units = "in", w = 6, h = 5)
```

In blue the individuals with outlying behaviour:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  geom_line(data = dat %>%
              filter(Ps %in% ell_1),
            aes(y = exp(pred)),
            col = 4) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Clustering.

```{r}
ran_dist14 <- dist(ran[,1:2])
ran_clust14 <- hclust(ran_dist14, method = "ward.D2")
clus214 <- cutree(ran_clust14, 2)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust14), type = "fan",
     tip.color = cols[clus214],
     font = 1,
     edge.width = .7)

dat$cluster <- dat$Ps
levels(dat$cluster) <- paste("Cluster", clus214)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ cluster)
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss2 <- NULL
for(i in 1:10) {
  twss2[i] <- sum(sumPartition(ran[,1:2], cutree(ran_clust14, i))[,2])
}

plot(twss2, type = "b")
```

### Stopping at trial 6

```{r}
dat <- read_csv("virtual_navigation_task.csv")

dat$Ps <- as.factor(dat$Ps)
dat$cens <- ifelse(dat$Score == 60, 0, 1)

dat <- dat %>%
  filter(Trial <= 6)
```

```{r, echo = FALSE}
gen.cens(GA)

fit1 <- gamlss(Surv(time = Score, event = cens, type = "right") ~
                 Trial + re(random = list(Ps = pdDiag(~ Trial))),
               sigma.formula = ~ Trial,
               family = cens(GA),
               data = dat)
summary(fit1)

getSmo(fit1)
```

Diagnostics:

```{r}
wp(fit1)

ran <- ranef(getSmo(fit1)) %>% as_tibble
names(ran) <- c("intercept","slope")
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- coef(fit1)[-length(coef(fit1))]
V <- vcov(fit1)[1:2,1:2]
dat_pred <- expand.grid(Trial = seq(1, 12, length = 200)) %>%
  as_tibble
X_pred <- model.matrix(~ Trial, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2)
```

Individual curves:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Producing ellipsoids.

```{r}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  xlab("Intercept") +
  ylab("Slope")

build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell1 <- build[[6]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

ell_1 <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))

ell1 <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ell1_centre <- c(mean(ell1$x),mean(ell1$y))
dist_ell1 <- apply(ell1, 1, function(x) dist_2_points(x, ell1_centre))

a_ell1 <- max(dist_ell1)
b_ell1 <- min(dist_ell1)
area_ell1 <- pi * a_ell1 * b_ell1
axis_ratio_ell1 <- a_ell1 / b_ell1
ecc_ell1 <- sqrt(1 - b_ell1^2/a_ell1^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

#ggsave("continuous_censored_new_t6.png", dpi = 800, units = "in", w = 6, h = 5)
```

In blue the individuals with outlying behaviour:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  geom_line(data = dat %>%
              filter(Ps %in% ell_1),
            aes(y = exp(pred)),
            col = 4) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Clustering.

```{r}
ran_dist <- dist(ran[,1:2])
ran_clust <- hclust(ran_dist, method = "ward.D2")
clus2 <- cutree(ran_clust, 2)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust), type = "fan",
     tip.color = cols[clus2],
     font = 1,
     edge.width = .7)

dat$cluster <- dat$Ps
levels(dat$cluster) <- paste("Cluster", clus2)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ cluster)
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss3 <- NULL
for(i in 1:10) {
  twss3[i] <- sum(sumPartition(ran[,1:2], cutree(ran_clust, i))[,2])
}

plot(twss3, type = "b")
```

### Stopping at trial 8

```{r}
dat <- read_csv("virtual_navigation_task.csv")

dat$Ps <- as.factor(dat$Ps)
dat$cens <- ifelse(dat$Score == 60, 0, 1)

dat <- dat %>%
  filter(Trial <= 8)
```

```{r, echo = FALSE}
gen.cens(GA)

fit1 <- gamlss(Surv(time = Score, event = cens, type = "right") ~
                 Trial + re(random = list(Ps = pdDiag(~ Trial))),
               sigma.formula = ~ Trial,
               family = cens(GA),
               data = dat)
summary(fit1)

getSmo(fit1)
```

Diagnostics:

```{r}
wp(fit1)

ran <- ranef(getSmo(fit1)) %>% as_tibble
names(ran) <- c("intercept","slope")
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- coef(fit1)[-length(coef(fit1))]
V <- vcov(fit1)[1:2,1:2]
dat_pred <- expand.grid(Trial = seq(1, 12, length = 200)) %>%
  as_tibble
X_pred <- model.matrix(~ Trial, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2)
```

Individual curves:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Producing ellipsoids.

```{r}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  xlab("Intercept") +
  ylab("Slope")

build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell1 <- build[[6]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

ell_1 <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))

ell1 <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ell1_centre <- c(mean(ell1$x),mean(ell1$y))
dist_ell1 <- apply(ell1, 1, function(x) dist_2_points(x, ell1_centre))

a_ell1 <- max(dist_ell1)
b_ell1 <- min(dist_ell1)
area_ell1 <- pi * a_ell1 * b_ell1
axis_ratio_ell1 <- a_ell1 / b_ell1
ecc_ell1 <- sqrt(1 - b_ell1^2/a_ell1^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

#ggsave("continuous_censored_new_t8.png", dpi = 800, units = "in", w = 6, h = 5)
```

In blue the individuals with outlying behaviour:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  geom_line(data = dat %>%
              filter(Ps %in% ell_1),
            aes(y = exp(pred)),
            col = 4) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Clustering.

```{r}
ran_dist <- dist(ran[,1:2])
ran_clust <- hclust(ran_dist, method = "ward.D2")
clus2 <- cutree(ran_clust, 2)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust), type = "fan",
     tip.color = cols[clus2],
     font = 1,
     edge.width = .7)

dat$cluster <- dat$Ps
levels(dat$cluster) <- paste("Cluster", clus2)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ cluster)
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss4 <- NULL
for(i in 1:10) {
  twss4[i] <- sum(sumPartition(ran[,1:2], cutree(ran_clust, i))[,2])
}

plot(twss4, type = "b")
```

### Stopping at trial 10

```{r}
dat <- read_csv("virtual_navigation_task.csv")

dat$Ps <- as.factor(dat$Ps)
dat$cens <- ifelse(dat$Score == 60, 0, 1)

dat <- dat %>%
  filter(Trial <= 10)
```

```{r, echo = FALSE}
gen.cens(GA)

fit1 <- gamlss(Surv(time = Score, event = cens, type = "right") ~
                 Trial + re(random = list(Ps = pdDiag(~ Trial))),
               sigma.formula = ~ Trial,
               family = cens(GA),
               data = dat)
summary(fit1)

getSmo(fit1)
```

Diagnostics:

```{r}
wp(fit1)

ran <- ranef(getSmo(fit1)) %>% as_tibble
names(ran) <- c("intercept","slope")
ran$ID <- 1:nrow(ran)

par(mfrow = c(2,2))
hnp(ran$intercept, scale = TRUE, main = "intercept")
hnp(ran$slope, scale = TRUE, main = "slope")
hist(ran$intercept, prob = TRUE, main = "intercept")
lines(density(ran$intercept))
curve(dnorm(x, 0, sd(ran$intercept)), add = TRUE, col = 4, lwd = 2)
hist(ran$slope, prob = TRUE, main = "slope")
lines(density(ran$slope))
curve(dnorm(x, 0, sd(ran$slope)), add = TRUE, col = 4, lwd = 2)
```

Predicted curve:

```{r}
beta_hat <- coef(fit1)[-length(coef(fit1))]
V <- vcov(fit1)[1:2,1:2]
dat_pred <- expand.grid(Trial = seq(1, 12, length = 200)) %>%
  as_tibble
X_pred <- model.matrix(~ Trial, data = dat_pred)
dat_pred$pred <- exp(X_pred %*% beta_hat) %>% as.numeric
se_pred <- sqrt(diag(X_pred %*% V %*% t(X_pred))) %>% as.numeric
dat_pred$lower <- exp(X_pred %*% beta_hat + qnorm(.025) * se_pred) %>% as.numeric
dat_pred$upper <- exp(X_pred %*% beta_hat + qnorm(.975) * se_pred) %>% as.numeric

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .2) +
  xlab("Trial") +
  ylab("Score") +
  geom_line(data = dat_pred, aes(y = pred),
            col = 4, lwd = 1) +
  geom_ribbon(data = dat_pred,
              aes(y = pred, ymin = lower, ymax = upper),
              fill = 4, alpha = .2)
```

Individual curves:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Producing ellipsoids.

```{r}
p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = "Shaded area represents 95% ellipsoid based on the bivariate normal distribution") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm",
               segments = 1000) +
  xlab("Intercept") +
  ylab("Slope")

build <- ggplot_build(p)$data
points1 <- build[[1]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)
ell1 <- build[[6]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

ell_1 <- which(as.logical(1 - point.in.polygon(points1$x, points1$y, ell1$x, ell1$y)))

ell1 <- build[[5]] %>% filter(PANEL == 1) %>% dplyr::select(x,y)

dist_2_points <- function(x1, x2) {
  return(sqrt(sum((x1 - x2)^2)))    
}

ell1_centre <- c(mean(ell1$x),mean(ell1$y))
dist_ell1 <- apply(ell1, 1, function(x) dist_2_points(x, ell1_centre))

a_ell1 <- max(dist_ell1)
b_ell1 <- min(dist_ell1)
area_ell1 <- pi * a_ell1 * b_ell1
axis_ratio_ell1 <- a_ell1 / b_ell1
ecc_ell1 <- sqrt(1 - b_ell1^2/a_ell1^2)
```

```{r}
final_p <- ran %>%
  ggplot(aes(x = intercept, y = slope)) +
  theme_bw() +
  geom_text_repel(data = ran %>%
                    filter(ID %in% ell_1),
                  aes(label = ID), force = .25) +
  geom_point(alpha = .5) +
  geom_vline(xintercept = 0, lty = 2) +
  geom_hline(yintercept = 0, lty = 2) +
  ggtitle("Random effects per individual",
          subtitle = paste0("95% ellipse area = ", round(area_ell1, 3),
                            "; eccentricity = ", round(ecc_ell1, 3))) +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .95,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .90,
               lty = 2, col = 4, type = "norm") +
  stat_ellipse(geom = "polygon", fill = 4,
               alpha = .2, level = .85,
               lty = 2, col = 4, type = "norm") +
  xlab("Intercept") +
  ylab("Slope") +
  labs(caption = "Shaded areas represents 95%, 90% and 85% ellipsoids based on the bivariate normal distribution")

print(final_p)

#ggsave("continuous_censored_new_t10.png", dpi = 800, units = "in", w = 6, h = 5)
```

In blue the individuals with outlying behaviour:

```{r}
dat$pred <- predict(fit1)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line() +
  geom_line(aes(y = exp(pred)),
            col = 2) +
  geom_line(data = dat %>%
              filter(Ps %in% ell_1),
            aes(y = exp(pred)),
            col = 4) +
  xlab("Trial") +
  ylab("Score") +
  facet_wrap(~ Ps)
```

Clustering.

```{r}
ran_dist <- dist(ran[,1:2])
ran_clust <- hclust(ran_dist, method = "ward.D2")
clus2 <- cutree(ran_clust, 2)
cols <- gg_color_hue(2)

plot(as.phylo(ran_clust), type = "fan",
     tip.color = cols[clus2],
     font = 1,
     edge.width = .7)

dat$cluster <- dat$Ps
levels(dat$cluster) <- paste("Cluster", clus2)

dat %>%
  ggplot(aes(x = Trial, y = Score)) +
  theme_bw() +
  geom_line(aes(group = Ps), alpha = .5) +
  xlab("Trial") +
  ylab("Score") +
  geom_smooth(col = 4) +
  facet_wrap(~ cluster)
```

Checking Total Within Cluster Sum of Squares for different numbers of clusters.

```{r}
twss5 <- NULL
for(i in 1:10) {
  twss5[i] <- sum(sumPartition(ran[,1:2], cutree(ran_clust, i))[,2])
}

plot(twss5, type = "b")
```

## Figure 3

```{r}
twss <- tibble(twss = c(twss1, twss2, twss3, twss4, twss5),
               trials = factor(rep(c("1 - 4","1 - 6","1 - 8","1 - 10","1 - 12"), each = 10), levels = c("1 - 4","1 - 6","1 - 8","1 - 10","1 - 12")),
               nclust = rep(1:10, 5))

dendro_data_k <- function(hc, k) {
  
  hcdata    <-  ggdendro::dendro_data(hc, type = "rectangle")
  seg       <-  hcdata$segments
  labclust  <-  cutree(hc, k)[hc$order]
  segclust  <-  rep(0L, nrow(seg))
  heights   <-  sort(hc$height, decreasing = TRUE)
  height    <-  mean(c(heights[k], heights[k - 1L]), na.rm = TRUE)
  
  for (i in 1:k) {
    xi      <-  hcdata$labels$x[labclust == i]
    idx1    <-  seg$x    >= min(xi) & seg$x    <= max(xi)
    idx2    <-  seg$xend >= min(xi) & seg$xend <= max(xi)
    idx3    <-  seg$yend < height
    idx     <-  idx1 & idx2 & idx3
    segclust[idx] <- i
  }
  
  idx                    <-  which(segclust == 0L)
  segclust[idx]          <-  segclust[idx + 1L]
  hcdata$segments$clust  <-  segclust
  hcdata$segments$line   <-  as.integer(segclust < 1L)
  hcdata$labels$clust    <-  labclust
  
  hcdata
}

set_labels_params <- function(nbLabels,
                              direction = c("tb", "bt", "lr", "rl"),
                              fan       = FALSE) {
  if (fan) {
    angle       <-  360 / nbLabels * 1:nbLabels + 90
    idx         <-  angle >= 90 & angle <= 270
    angle[idx]  <-  angle[idx] + 180
    hjust       <-  rep(0, nbLabels)
    hjust[idx]  <-  1
  } else {
    angle       <-  rep(0, nbLabels)
    hjust       <-  0
    if (direction %in% c("tb", "bt")) { angle <- angle + 45 }
    if (direction %in% c("tb", "rl")) { hjust <- 1 }
  }
  list(angle = angle, hjust = hjust, vjust = 0.5)
}

plot_ggdendro <- function(hcdata,
                          direction   = c("lr", "rl", "tb", "bt"),
                          fan         = FALSE,
                          scale.color = NULL,
                          branch.size = 1,
                          label.size  = 3,
                          nudge.label = 0.01,
                          expand.y    = 0.1) {
  
  direction <- match.arg(direction) # if fan = FALSE
  ybreaks   <- pretty(segment(hcdata)$y, n = 5)
  ymax      <- max(segment(hcdata)$y)
  
  ## branches
  p <- ggplot() +
    geom_segment(data         =  segment(hcdata),
                 aes(x        =  x,
                     y        =  y,
                     xend     =  xend,
                     yend     =  yend,
                     colour   =  factor(clust)),
                 lineend      =  "round",
                 show.legend  =  FALSE,
                 size         =  branch.size)
  
  ## orientation
  if (fan) {
    p <- p +
      coord_polar(direction = -1) +
      scale_x_continuous(breaks = NULL,
                         limits = c(0, nrow(label(hcdata)))) +
      scale_y_reverse(breaks = ybreaks)
  } else {
    p <- p + scale_x_continuous(breaks = NULL)
    if (direction %in% c("rl", "lr")) {
      p <- p + coord_flip()
    }
    if (direction %in% c("bt", "lr")) {
      p <- p + scale_y_reverse(breaks = ybreaks)
    } else {
      p <- p + scale_y_continuous(breaks = ybreaks)
      nudge.label <- -(nudge.label)
    }
  }
  
  # labels
  labelParams <- set_labels_params(nrow(hcdata$labels), direction, fan)
  hcdata$labels$angle <- labelParams$angle
  
  p <- p +
    geom_text(data        =  label(hcdata),
              aes(x       =  x,
                  y       =  y,
                  label   =  label,
                  colour  =  factor(label2),
                  angle   =  angle),
              vjust       =  labelParams$vjust,
              hjust       =  labelParams$hjust,
              nudge_y     =  ymax * nudge.label,
              size        =  label.size,
              show.legend =  FALSE)
  
  if (!is.null(scale.color)) {
    p <- p + scale_color_manual(values = scale.color)
  }
  
  ylim <- -round(ymax * expand.y, 1)
  p    <- p + expand_limits(y = ylim)
  
  p
}

dend_col <- gg_color_hue(2)
ddata14 <- dendro_data_k(ran_clust14, 2)
ddata112 <- dendro_data_k(ran_clust112, 2)

fig3_d <- twss %>%
  filter(nclust <= 7) %>%
  ggplot(aes(y = twss, x = nclust)) +
  theme_bw() +
  geom_point() +
  geom_line() +
  xlab("Number of clusters") +
  ylab("TWSS") +
  scale_x_continuous(breaks = 1:7) +
  facet_wrap(~ trials) +
  ggtitle("(d) Within cluster sums of squares")

ddata14$labels$label2 <- ddata14$labels$clust
ddata112$labels$label2 <- ddata112$labels$clust

fig3_e <- plot_ggdendro(ddata14,
              fan = TRUE,
              label.size = 4.5,
              expand.y = .1,
              branch.size = .4) +
  theme_void() +
  ggtitle("(e) Clustering individuals: Trials 1 - 4")

fig3_f <- plot_ggdendro(ddata112,
              fan = TRUE,
              label.size = 4.5,
              expand.y = .1,
              branch.size = .4) +
  theme_void() +
  ggtitle("(f) Clustering individuals: Trials 1 - 12")
```

```{r}
# to combine all subparts as one figure
# library(gridExtra)
# png("fig3.png", w = 12, h = 12, res = 800, units = "in")
# grid.arrange(fig3_a, fig3_b, fig3_c, fig3_d, fig3_e, fig3_f, ncol = 2)
# dev.off()
```